### 2017-05-30 02-02-related.tex
Replace D-KV with DKV

\begin{comment}
In this paper, we describe our custom RDMA D-KV (Distributed Key-Value)
store. Current RMDA D-KV store implementations are RamCloud~\cite{RamCloud},
Pilaf~\cite{Pilaf}, Herd~\cite{Herd} and FaRM~\cite{FaRM}. All these systems
use RDMA to implement a D-KV store. However, all of them are far more powerful
than our custom implementation -- and this power comes at a cost that we
can avoid. They implement a generic D-KV store that controls concurrency,
supports dynamic inserts and deletes, supports variable-sized values
(whose size may change at an update), and keys of arbitrary type. Because
of the nature of our distributed algorithm, we have to deal with none of
these issues. For us, values are fixed-size, allocated only at the initial
population, and remain alive forever. We have no concurrency between writes
and reads or other writes. Our keys are a contiguous range of integers. All
these properties together allow an extremely low-overhead implementation
that does not involve the remote host in any transaction.
\end{comment}

@@

\textbf{\emph{QUESTION: Re-insert related work on RDMA KV stores?}}
\begin{comment}
\subsection{Related work on RDMA Key-Value stores}
In this paper, we describe our custom RDMA D-KV (Distributed Key-Value)
store. Current RMDA D-KV store implementations are RamCloud~\cite{RamCloud},
Pilaf~\cite{Pilaf}, Herd~\cite{Herd} and FaRM~\cite{FaRM}. All these systems
use RDMA to implement a D-KV store. However, all of them are far more powerful
than our custom implementation -- and this power comes at a cost that we
can avoid. They implement a generic D-KV store that controls concurrency,
supports dynamic inserts and deletes, supports variable-sized values
(whose size may change at an update), and keys of arbitrary type. Because
of the nature of our distributed algorithm, we have to deal with none of
these issues. For us, values are fixed-size, allocated only at the initial
population, and remain alive forever. We have no concurrency between writes
and reads or other writes. Our keys are a contiguous range of integers. All
these properties together allow an extremely low-overhead implementation
that does not involve the remote host in any transaction.
\end{comment}

>>>>

\begin{comment}
In this paper, we describe our custom RDMA DKV (Distributed Key-Value)
store. Current RMDA DKV store implementations are RamCloud~\cite{RamCloud},
Pilaf~\cite{Pilaf}, Herd~\cite{Herd} and FaRM~\cite{FaRM}. All these systems
use RDMA to implement a DKV store. However, all of them are far more powerful
than our custom implementation -- and this power comes at a cost that we
can avoid. They implement a generic DKV store that controls concurrency,
supports dynamic inserts and deletes, supports variable-sized values
(whose size may change at an update), and keys of arbitrary type. Because
of the nature of our distributed algorithm, we have to deal with none of
these issues. For us, values are fixed-size, allocated only at the initial
population, and remain alive forever. We have no concurrency between writes
and reads or other writes. Our keys are a contiguous range of integers. All
these properties together allow an extremely low-overhead implementation
that does not involve the remote host in any transaction.
\end{comment}

@@

\textbf{\emph{QUESTION: Re-insert related work on RDMA KV stores?}}
\begin{comment}
\subsection{Related work on RDMA Key-Value stores}
In this paper, we describe our custom RDMA DKV (Distributed Key-Value)
store. Current RMDA DKV store implementations are RamCloud~\cite{RamCloud},
Pilaf~\cite{Pilaf}, Herd~\cite{Herd} and FaRM~\cite{FaRM}. All these systems
use RDMA to implement a DKV store. However, all of them are far more powerful
than our custom implementation -- and this power comes at a cost that we
can avoid. They implement a generic DKV store that controls concurrency,
supports dynamic inserts and deletes, supports variable-sized values
(whose size may change at an update), and keys of arbitrary type. Because
of the nature of our distributed algorithm, we have to deal with none of
these issues. For us, values are fixed-size, allocated only at the initial
population, and remain alive forever. We have no concurrency between writes
and reads or other writes. Our keys are a contiguous range of integers. All
these properties together allow an extremely low-overhead implementation
that does not involve the remote host in any transaction.
\end{comment}

### 2017-05-30 distr-04-evaluation.tex
Replace D-KV with DKV

\begin{figure}[tb] % [htbp]
  \centering
  \epsfig{file=plots/qperf.eps, width=\columnwidth}
  \caption{Performance of DKV store vs.\ \textit{qperf} and MPI roundtrip.}
  \label{fig-qperf}
\end{figure}

@@

Since the distributed algorithm is data-intensive, a key aspect in improving
its performance is to maximize the utility of the network resources.
In Figure~\ref{fig-qperf}, we provide maximum bandwidth numbers for
read operations between one server and one client for a range of payload sizes,
and compare these to the bandwidth achieved by an MPI roundtrip test,
and by \textit{qperf}~\cite{qperf-mellanox} which reports
the best achievable performance for Infiniband. We present \textit{qperf}
bandwidth for both RDMA read and RDMA write operations; these are quite
close, which corroborates the results from the Herd project for payloads
upwards from 256B.
The OpenMPI implementation has an ib-verbs implementation for Infiniband,
hence it has very good performance.
The MPI benchmark requires an interaction between
the server network card and the server host, which increases the latency and
thus lowers the bandwidth
significantly.
Note that the comparison is
lopsided: \textit{qperf} and MPI are low-level point-to-point benchmarks without
any DKV store implementation on top.
The performance presented in this Figure
is ample justification for using a low-level RDMA
implementation for the DKV store.
The bandwidth achieved by our DKV store falls short
of the \textit{qperf} performance for packets less than 4KB; this is attributed
to additional per-request overhead for the DKV store. For the largest packet
size, the DKV store performance is hampered by the fact that its values
are spread over a larger memory area, whereas \textit{qperf} and MPI always read
from the same memory locations. For packets between 8KB and 512KB, our DKV
store achieves performance very close to \textit{qperf}.

%################################################
\subsubsection{Convergence of Large Datasets}

>>>>

\begin{figure}[tb] % [htbp]
  \centering
  \epsfig{file=plots/qperf.eps, width=\columnwidth}
  \caption{Performance of DKV store vs.\ \textit{qperf} and MPI round-trip.}
  \label{fig-qperf}
\end{figure}

@@

Since the distributed algorithm is data-intensive, a key aspect in improving
its performance is to maximize the utility of the network resources.
In Figure~\ref{fig-qperf}, we provide maximum bandwidth numbers for
read operations between one server and one client for a range of payload sizes,
and compare these to the bandwidth achieved by an MPI round-trip test,
and by \textit{qperf}~\cite{qperf-mellanox} which reports
the best achievable performance for Infiniband. We present \textit{qperf}
bandwidth for both RDMA read and RDMA write operations; these are quite
close, which corroborates the results from the Herd project for payloads
upwards from 256B.
The OpenMPI implementation has an ib-verbs implementation for Infiniband,
hence it has very good performance.
The MPI benchmark requires an interaction between
the server network card and the server host, which increases the latency and
thus lowers the bandwidth
significantly.
Note that the comparison is
lopsided: \textit{qperf} and MPI are low-level point-to-point benchmarks without
any DKV store implementation on top.
The performance presented in this Figure
is ample justification for using a low-level RDMA
implementation for the DKV store.
The bandwidth achieved by our DKV store falls short
of the \textit{qperf} performance for packets less than 4KB; this is attributed
to additional per-request overhead for the DKV store. For the largest packet
size, the DKV store performance is hampered by the fact that its values
are spread over a larger memory area, whereas \textit{qperf} and MPI always read
from the same memory locations. For packets between 8KB and 512KB, our DKV
store achieves performance very close to \textit{qperf}.

%################################################
\subsubsection{Convergence of Large Data sets}
